\datedsubsection{2023}
		{%
			organized by the Society for Molecular Biology and Evolution, held in Ferrara, Italy.
        }
		{%
		    SMBE2023
        }
		{%
        Talk title: Shared evolutionary processes shape genomic variation in the great apes. \href{https://github.com/mufernando/smbe2023}{See slides here.}
        }
\datedsubsection{2022}
		{%
			organized by the Genetics Society of America, held in Californa, United States.
        }
		{%
		    Population, Evolutionary, and Quantitative Genetics Conference
        }
		{%
        Poster title: Why are landscapes of diversity correlated in the great apes? \href{https://github.com/mufernando/peqg2022}{See poster here.}
        }
\datedsubsection{2021}
		{%
			organized by the Society for Molecular Biology and Evolution, held virtually.
        }
		{%
		    SMBEv2021
        }
		{%
        Poster title: Natural selection and landscapes of diversity in the great apes.
        }

\datedsubsection{2021}
		{%
			organized by Cold Spring Harbor Laboratories, held virtually.
        }
		{%
		    Probabilistic Modeling in Genomics
        }
		{%
        Poster title: Natural selection and landscapes of diversity in the great apes. \href{https://github.com/mufernando/probgen21}{See poster here.}
        }

\datedsubsection{2020}
		{%
			organized by the Genetics Society of America, held virtually.
        }
		{%
		    The Allied Genetics Conference
        }
		{%
        }

\datedsubsection{2014}
		{%
			Universidade de São Paulo, Brasil
        }
		{%
		    8th Workshop on Cestode Systematics and Phylogeny
        }
		{%
        }

